Which object-oriented architectures could best support QOS-oriented map streaming in a multiplayer persistent C++ game?

### 2018-02-27 proposal.tex
WIP new proposal files

\title{Which packet compression techniques for player synchronisation are ideal for improving speed and reducing bandwidth in large-scale multi-player games?}
\subtitle{COMP130 - Computing Architecture}
\date{\today}
\author{1707981}

@@

\section{Proposal}
The exponential bandwidth consumption resulting by distributing player data in large-scale multi-player games is a significant challenge to game developers. Server maintenance costs are high as a consequence of high bandwidth use. Furthermore, a high percentage of UK homes run on a broadband speed at around 15Mbps, which roughly translates.

This study is interested in finding new ways, in many places drawing inspiration from the recent and highly successful temporal video compression techniques achieved as a reaction to the growth of streaming services such as YouTube.

To identify potential costs, this study will first aim to discover the presently known costs of game server maintenance. This will help us understand how much could be gained or lost from a reduction in network packet traffic, and thus how much time, money and effort a company may invest in combating the issue.

Following this, the study will attempt to uncover present weaknesses in common practices. This will share technical insight into the most significant bottlenecks common in today's online games. A particular genre of interest is the MMO genre, as well as the growing `battle royale', genre both of which can enjoy masses of players synchronised in a single world. These games are particularly vulnerable to exponential bandwidth congestion due to the player traffic sent from each player to each other player.

Finally, it will propose techniques to reduce packet consumption. This may include existing game networking techniques, image compression, and video compression or streaming strategies.

Video compression is a particular area of interest, owing to its temporal nature: frames are compressed not in absolute terms, but relative to the previous frame. This is not unlike the changes in player states as they progress through a game, although the specific types of data are quite different. Whether or not image data compression can be transferred to player data for any specific technique will be carefully considered throughout the essay.

The rapid advancement of the video compression domains could expose new opportunities in the game industry to efficiently compress and distribute update packets in previously unexplored ways. Should this happen, it may reveal the possibility for larger-scale persistent multi-player games to be created at a reasonable and sustainable cost for the interested game developer.

\bibliography{references} 
\bibliographystyle{ieeetr}

>>>>

\title{Which object-oriented architectures could best support QOS-oriented map streaming in a multiplayer persistent C++ game?}
\subtitle{COMP130 - Computing Architecture}
\date{\today}
\author{1707981}

@@

Games to lookup: Barotrauma, Doom 3?

\section{Proposal}
Free-to-play multiplayer games enjoy a high popularity in poorer countries such as China, Brazil and Mexico, yet the lower broadband speeds in these areas can pose a particular challenge to games with persistent player-driven worlds. These types of worlds require the server to upload level data to each player periodically, such that they can see the current version of an area as they enter it.

Unfortunately, broadband network speeds remain notoriously unreliable especially in developing countries. In order for games to be available to this wider market, they must utilise ways to reduce bandwidth while still providing enough data for the game to be playable.

Quality-of-service encompasses the concept of restricting traffic in high bandwidth scenarios such that the data most useful to the player is prioritised. However, to utilise such a system, a game's internal architecture--including class structure, design patterns--must be prepared to function with incomplete data.

This essay explores the application of design patterns to quality-of-service streaming in games. First, the significance and impact of low bandwidth on the player's end will be explored and challenged. Then, previous methods and architectures employed by companies in the past will be identified. This includes traditional single-player system architectures employed by successful games, followed by those employed by multiplayer games. A point of interest is whether there is an existing difference. Finally, this essay will compare the most popular architectures in general and attempt to theoretically deduce
 which may be the most efficient
\nocite{*}
\bibliography{references} 
\bibliographystyle{ieeetr}
